Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2023-07-25 Rdocs/ManuscriptLPP.Rmd
moved plot source code to the Manuscript RMD file moved plots ot Manuscript RMD file standardized which data table is used in plot source code cleaned up depedency packages for each script

---
title: Biodegradable alternatives to plastic mesh bags conventionally used in freshwater
  macroinvertebrate analysis within the Bronx River, NYC
author: "R.E. Segui-Baez, G.A. Rueda Moreno, R. Ward, K. Schneider Paolantonio"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
#knitr options----
knitr::opts_chunk$set(echo = TRUE)
#dependencies----
require(GGally)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

@@

## Including Plots

You can also embed plots, for example:

```{r plots, echo=FALSE}
ggpairs(select(bd_list$biodiversity, MidgeFlies:Planaria))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: Biodegradable alternatives to plastic mesh bags conventionally used in freshwater
  macroinvertebrate analysis within the Bronx River, NYC
author: "R.E. Segui-Baez, G.A. Rueda Moreno, R. Ward, K. Schneider Paolantonio"
date: "`r Sys.Date()`"
output: word_document
bibliography: references.bib
---

```{r setup, include=FALSE}
#knitr options----
knitr::opts_chunk$set(echo = TRUE)
#dependencies----
require(tidyverse)
require(GGally)
require(vegan)
require(ggpubr)
require(tidyverse)
require(viridisLite)
require(rlang)
require(car)
require(corrplot)
require(factoextra)

#plotting source code----
#set plotting theme function 
theme_rafa <- function(base_size){
  theme_pubr(base_family="sans") %+replace%
    theme(panel.background  = element_blank(),
          plot.background = element_rect(fill="transparent", colour=NA), 
          legend.background = element_rect(fill="transparent", colour=NA),
          legend.key = element_rect(fill="transparent", colour=NA),
          legend.text = element_text(size=base_size * 0.7),
          legend.title = element_text(size = base_size * 0.8, 
                                      face = "bold"),
          axis.text = element_text(size = base_size*0.85),
          axis.title = element_text(size = base_size * 1.2),
          plot.title.position = "panel",
          plot.caption.position = "panel",
          plot.title = element_text(
            size = base_size * 1.25,
            face = "bold", 
            hjust = 0.5,
            vjust = 1),
          plot.subtitle = element_text(
            size = base_size * 0.9,
            vjust = 1),
          plot.caption =  element_text(
            size = base_size*0.75,
            hjust = 0.5)
    )
}

#bag type barplot function:
#PARAMS: 
  #index(string): a string specifying the desired index

bt_barplot <- function(index){
  #calculate mean and standard error of chosen index
  new_tbl <- LPP_FullData%>%
  filter(is.na(material) == FALSE)%>% #remove na values from material before calculations
    group_by(material) %>% #group by material
    mutate(index_se = sd(get(index), na.rm = T)/sqrt(n())) %>% # calc SE
    summarise(index = mean(get(index), na.rm = T), index_se = mean(index_se)) #summarise into mean

  ggplot(new_tbl, aes(x = reorder(material, -index, sum), y = index)) +
    geom_col(aes(fill = reorder(material, -index, sum))) +
    geom_errorbar(aes(ymin = index - 2*index_se, ymax = index + 2*index_se)) +

    theme_bw() +
    scale_fill_viridis_d(begin = 0.1, end = 0.9)+
    theme_rafa(base_size = 15) +
    theme(axis.text.x = element_text(angle = -15, vjust = 0.5))+
    labs(x = "material", title = "Diversity Index by Bag material", y = paste(index),
         fill = "material")
}

#water quality time series plots by site
#PARAMS:
  #param(string): a string specifying the water quality parameter

wq_ts_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call
  param<- sym(param)
  param_se <- sym(paste(param,"se", sep = "_"))
  ggplot(LPP_FullData, aes(x = date, y = !!param, color = site)) +
    #geom layers
    geom_point() +
    geom_errorbar(aes(ymin = !!param - 2*!!param_se, ymax = !!param + 2*!!param_se)) + 
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_color_viridis_d(begin = 0.1, end = 0.9)
}
```

##Abstract

##Introduction

##Methods

###Study Site and Timescale

###Leaf Packs: Preparation

###Leaf Packs: Retrieval and Sorting

###Water Quality

###Data Analyses

@@

##Results

```{r result plots, echo=FALSE}
#biodiversity plots----
#cummul richness bag type barplots
bt_barplot( "shannon")+ labs(x = "Material", y= "Shannon Diversity")
bt_barplot( "simpson")+ labs(x = "Material",y= "Simpson Diversity")
bt_barplot( "invsimp")+ labs(x = "Material",y= "Inverse-Simpson Diversity")
bt_barplot( "richness")+ labs(x = "Material", y="Richness")
bt_barplot("even")+ labs(x = "Material",y= "Shannon Evenness")

#water quality dot plots
#water quality by date on the y and site as color
wq_ts_BySite("P")
wq_ts_BySite("pH")
wq_ts_BySite("NH3")
wq_ts_BySite("DO")
wq_ts_BySite("Temp")
wq_ts_BySite("Cond")
wq_ts_BySite("Nitrogen")
wq_ts_BySite("Flow") + labs(title = "Flow rate seasonality",
                            x = "Date", y = "Flow (m/s)")
ggpairs(select(bd_list$biodiversity, MidgeFlies:Planaria))
```

##Discussion

##Acknowledgements

##Referrences
